Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-05-17 ms.tex
added an example pixel-wise time series.

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.37\columnwidth]{ap_labels_row_by_row_group_sub_aps_1_NRCALONG-DARK-7235074213_1}
\includegraphics[width=.37\columnwidth]{ap_labels_darkRedsmoothedRowKernel_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.37\columnwidth]{zoom_long_dark_row_by_row_group_sub.pdf}
\includegraphics[width=.37\columnwidth]{zoom_long_dark_darkRedsmoothedRowKernel.pdf}
\caption{The same apertures as Figure \ref{fig:longDarkPhot}, but with subtraction by a smoothed image where a 40 pixel wide and 1 pixel tall averaging kernel was applied along the fast read direction of every group.
Subtraction by the smoothed image has a dramatic effect on reducing correlated 1/f read noise from $\sim$6,000 DN to $\sim$700 DN in the aperture.
}\label{fig:longDarkWithRowKernel}
\end{figure*}
\clearpage

>>>>

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.37\columnwidth]{ap_labels_row_by_row_group_sub_aps_1_NRCALONG-DARK-7235074213_1}
\includegraphics[width=.37\columnwidth]{ap_labels_darkRedsmoothedRowKernel_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.37\columnwidth]{zoom_long_dark_row_by_row_group_sub.pdf}
\includegraphics[width=.37\columnwidth]{zoom_long_dark_darkRedsmoothedRowKernel.pdf}
\caption{The same apertures as Figure \ref{fig:longDarkPhot}, but with subtraction by a smoothed image where a 40 pixel wide and 1 pixel tall averaging kernel was applied along the fast read direction of every group.
Subtraction by the smoothed image has a dramatic effect on reducing correlated 1/f read noise from $\sim$6,000 DN to $\sim$700 DN in the aperture.
}\label{fig:longDarkWithRowKernel}
\end{figure*}

\subsubsection{Other Reference Channel Subtraction}
We note that the 4 channels have very similar 1/f correlation behavior, as shown in Figure \ref{fig:darkPixelTimeSeries}.
Another option to remove 1/f noise is to subtract the illuminated amplifier with a target in it by unilluminated channels.

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{pixeltime_series.pdf}
\caption{The time series for all 4 amplifiers is very similar due to shared 1/f noise behavior.
This is visible in a short segment of the time series of all pixels for an example group up the ramp (53) in a dark ramp where the bias has already been subtracted.}\label{fig:darkPixelTimeSeries}
\end{figure*}

\clearpage
